Body size patterns

### 2019-07-26 MS_Analysis_3spp_4rivers_Patterns_from 2spp_bySpp.Rmd
cleaned up figs

ggplot(cohortStrength %>% filter(cohort > 1999), aes(cohort, cohortStrengthScaled, group = speciesGG, shape = speciesGG, color = speciesGG)) +
  geom_point(size = 2) +
  geom_line(size = 1.2) +
  labs(x = 'Cohort',
       y = 'Cohort strength',
       shape = 'Species', color='Species') +
  theme_publication() +
 # scale_fill_grey() +
  theme(legend.position = "right", 
    legend.direction = "vertical",
    legend.title = element_text(face = "plain")) +
  facet_grid(metaPop01 ~ .)

@@

ggplot(cohortStrengthWide %>% filter(cohort >= 2002), aes(cohortStrengthScaledBKT, cohortStrengthScaledBNT, color=factor(cohort))) +
  geom_point() +
  geom_smooth(method = 'lm', se = FALSE)

@@

ggplot(vB %>% filter(cohort %in% 2000:2013, species %in% c('bkt', 'bnt', 'ats')), aes(ydayCumul,observedLength)) +
  geom_point(size = 0.5, alpha = 0.1) +
 # geom_smooth(span = 0.1, size = 1.5, se = F) +
 # geom_smooth(method='gam', alpha=0.1, formula=y~s(x, k = kValue), se = F) +
  labs(y = 'Observed body size (mm)',
       x = 'Days since age-0 Jan 1') +
  facet_wrap(~ speciesGG) +
  theme_publication()

@@

ggplot(vB %>% filter(cohort %in% 2000:2013, species %in% c('bkt', 'bnt', 'ats'), !is.na(observedLength)),
       aes(riverGG, fill = speciesGG)) +
  geom_bar() +
  labs(x = 'River', y = 'Number of observations', fill = 'Species') +
  theme_publication() +
  scale_fill_grey() +
  theme(legend.position = "right", 
    legend.direction = "vertical",
    legend.title = element_text(face = "plain"))

@@

# cohorts by river/species
ggplot(predGrid2Both %>% 
         filter(salmon01 ==0, cohortStrengthScaledBKT == 0, cohortStrengthScaledBNT2p5 == 0
#         (cohortStrengthScaledBKT == 0 & salmon01 == 0) | (cohortStrengthScaledBKT == 0 & cohortStrengthScaledBNT == 0 & cohortStrengthScaledATS == 0 & metaPop01 == 1 & salmon01 ==0)
           ),
#           cohortStrengthScaledBKT == 0, cohortStrengthScaledBNT == 0, cohortStrengthScaledATS == 0, metaPop01 == 1, salmon01 == 0),
       aes(ydayCumul, pred, group = cohort, color = cohort)) +
  #geom_point() + 
  geom_vline(xintercept = c(365,365*2), color = 'grey60', linetype = 2) +
  geom_line(size = 1.1) +
  labs(y = 'Predicted body size (mm)',
       x = 'Days since age-0 Jan 1',
       color = 'Cohort') +
  scale_color_viridis_c(breaks = c(2000,2004,2008,2012), labels = c(2000,2004,2008,2012)) +
  theme_publication() +
  theme(legend.position = "right", 
        legend.direction = "vertical",
        legend.title = element_text(face = "plain")) +
  guides(color = guide_colorbar(barheight = 10,
                                barwidth = 1.5,
                                ticks = FALSE,
                                nbin = 100)) +
#  guide_legend(title = 'Cohort') +
  facet_grid(speciesGG ~ riverGG, scales = 'free_y')

@@

# specific spline effects by species
(plotCohort <- plotGamVarBySpecies(var = 's(cohort)', xAxisLab = 'Cohort'))
ggsave('./figures/cohortEffect.png', width = 11, height = 8, units='in')

(plotCohortStrength <- plotGamVarBySpecies(var = 's(cohortStrengthScaledBKT)', xAxisLab = 'Brook Trout cohort Strength'))
ggsave('./figures/cohortStrengthEffectBKT.png', width = 11, height = 8, units='in')

(plotCohortStrengthScaledBNT2p5 <- plotGamVarBySpecies(var = 's(cohortStrengthScaledBNT2p5)', xAxisLab = 'Brown Trout cohort Strength'))
ggsave('./figures/cohortStrengthEffectBNT.png', width = 11, height = 8, units='in')

@@

# across rivers, by species
ggplot(predGrid2Both %>% 
         filter(salmon01 == 0, cohortStrengthScaledBKT == 0, cohort == 2006, cohortStrengthScaledBNT2p5 == 0),
       aes(ydayCumul, pred, group = speciesGG, color = speciesGG)) +
  #geom_point() + 
  geom_vline(xintercept = c(365,365*2), color = 'grey60', linetype = 2) +
  geom_line(size = 1.1) +
  labs(y = 'Predicted body size (mm)',
       x = 'Days since age-0 Jan 1',
       color = 'Cohort') +
#  scale_color_viridis_c() +
  theme_publication() +
  theme(legend.position = "right", 
        legend.direction = "vertical",
        legend.title = element_text(face = "plain")) +
  facet_wrap(~ riverGG)

ggsave('./figures/ydayCumulAcrossRiverBySpp.png', width = 11, height = 8, units='in')

# across species, by rivers
ggplot(predGrid2Both %>% 
         filter(salmon01 == 0, cohortStrengthScaledBKT == 0, cohort == 2006, cohortStrengthScaledBNT2p5 == 0),
       aes(ydayCumul, pred, group = riverGG, color = riverGG)) +
  #geom_point() + 
  geom_vline(xintercept = c(365,365*2), color = 'grey60', linetype = 2) +
  geom_line(size = 1.1) +
  labs(y = 'Predicted body size (mm)',
       x = 'Days since age-0 Jan 1',
       color = 'River') +
  #scale_color_viridis_c() +
  theme_publication() +
  theme(legend.position = "right", 
        legend.direction = "vertical",
        legend.title = element_text(face = "plain")) +
  facet_grid(rows = vars(speciesGG))

ggsave('./figures/ydayCumulAcrossSppByRiver.png', width = 8, height = 8, units='in')

>>>>

ggplot(cohortStrength %>% filter(cohort > 1999), aes(cohort, cohortStrengthScaled, group = speciesGG, shape = speciesGG, color = speciesGG)) +
  geom_point(size = 3) +
  geom_line(size = 1.2) +
  labs(x = 'Cohort',
       y = 'Cohort strength',
       shape = 'Species', color='Species') +
  theme_publication(base_size = 20) +
  scale_color_grey() +
  theme(legend.position = "none",
        #legend.position=c(0.8, 0.8),
    #legend.direction = "vertical",
    #legend.title = element_text(face = "plain"),
    strip.background = element_blank(),
    strip.text.y = element_blank()) +
  facet_grid(metaPop01 ~ .)

@@

ggplot(cohortStrengthWide %>% filter(cohort >= 2002, metaPop01 == 1), aes(cohortStrengthScaledBKT, cohortStrengthScaledBNT)) +
  geom_point(size = 4) +
  geom_smooth(method = 'lm', se = FALSE, color = 'grey30') +
  theme_publication(base_size = 24) +
  labs(x = 'Brook Trout cohort strength',
       y = 'Brown Trout cohort strength') +
  theme(legend.position = "none")

ggsave('./figures/cohortStrengthBKT_BNT.png', width = 11, height = 8, units='in')

CS_bkt_bnt <- lm(cohortStrengthScaledBNT ~ cohortStrengthScaledBKT, data = cohortStrengthWide %>% filter(cohort >= 2002, metaPop01 == 1))

summary(CS_bkt_bnt)

@@

ggplot(vB %>% filter(cohort %in% 2000:2013, species %in% c('bkt', 'bnt', 'ats')), aes(ydayCumul,observedLength)) +
  geom_point(size = 0.5, alpha = 0.1) +
 # geom_smooth(span = 0.1, size = 1.5, se = F) +
 # geom_smooth(method='gam', alpha=0.1, formula=y~s(x, k = kValue), se = F) +
  labs(y = 'Observed body size (mm)',
       x = 'Days since age-0 Jan 1') +
  facet_wrap(~ speciesGG) +
  theme_publication(base_size = 20)

@@

ggplot(vB %>% filter(cohort %in% 2000:2013, species %in% c('bkt', 'bnt', 'ats'), !is.na(observedLength)),
       aes(riverGG, fill = speciesGG)) +
  geom_bar() +
  labs(x = 'River', y = 'Number of observations', fill = 'Species') +
  theme_publication(base_size = 24) +
  scale_fill_grey() +
  theme(#legend.position = "right", 
    legend.direction = "vertical",
    legend.title = element_text(face = "plain"),
    legend.position=c(0.8, 0.8))

@@

# cohorts by river/species
ggplot(predGrid2Both %>% 
         filter(salmon01 ==0, cohortStrengthScaledBKT == 0, cohortStrengthScaledBNT2p5 == 0
#         (cohortStrengthScaledBKT == 0 & salmon01 == 0) | (cohortStrengthScaledBKT == 0 & cohortStrengthScaledBNT == 0 & cohortStrengthScaledATS == 0 & metaPop01 == 1 & salmon01 ==0)
           ),
#           cohortStrengthScaledBKT == 0, cohortStrengthScaledBNT == 0, cohortStrengthScaledATS == 0, metaPop01 == 1, salmon01 == 0),
       aes(ydayCumul, pred, group = cohort, color = cohort)) +
  #geom_point() + 
  geom_vline(xintercept = c(365,365*2), color = 'grey60', linetype = 2) +
  geom_line(size = 1.1) +
  labs(y = 'Predicted body size (mm)',
       x = 'Days since age-0 Jan 1',
       color = 'Cohort') +
  scale_color_viridis_c(breaks = c(2000,2004,2008,2012), labels = c(2000,2004,2008,2012)) +
  theme_publication(base_size = 20) +
  theme(legend.position = "right", 
        legend.direction = "vertical",
        legend.title = element_text(face = "plain")) +
  guides(color = guide_colorbar(barheight = 10,
                                barwidth = 1.5,
                                ticks = FALSE,
                                nbin = 100)) +
#  guide_legend(title = 'Cohort') +
  facet_grid(speciesGG ~ riverGG, scales = 'free_y')

@@

# specific spline effects by species
(plotCohort <- plotGamVarBySpecies(var = 's(cohort)', xAxisLab = 'Cohort'))
ggsave('./figures/cohortEffect.png', width = 8, height = 8, units='in')

(plotCohortStrength <- plotGamVarBySpecies(var = 's(cohortStrengthScaledBKT)', xAxisLab = 'Brook Trout cohort Strength'))
ggsave('./figures/cohortStrengthEffectBKT.png', width = 8, height = 8, units='in')

(plotCohortStrengthScaledBNT2p5 <- plotGamVarBySpecies(var = 's(cohortStrengthScaledBNT2p5)', xAxisLab = 'Brown Trout cohort Strength'))
ggsave('./figures/cohortStrengthEffectBNT.png', width = 8, height = 4.75, units='in')

@@

# across rivers, by species
ggplot(predGrid2Both %>% 
         filter(salmon01 == 0, cohortStrengthScaledBKT == 0, cohort == 2006, cohortStrengthScaledBNT2p5 == 0, riverGG %in% c("West Brook", "Open Large")),
       aes(ydayCumul, pred, group = speciesGG)) +
  #geom_point() + 
  geom_vline(xintercept = c(365,365*2), color = 'grey60', linetype = 2) +
  geom_line(aes(linetype = speciesGG), size = 1.1) +
  labs(y = 'Predicted body size (mm)',
       x = 'Days since age-0 Jan 1',
       color = 'Cohort') +
#  scale_color_viridis_c() +
  theme_publication(base_size = 20) +
  #scale_color_grey() +
  theme(legend.position = "none", 
        legend.direction = "vertical",
        legend.title = element_text(face = "plain")) +
  facet_wrap(~ riverGG)

ggsave('./figures/ydayCumulAcrossRiverBySpp.png', width = 8, height = 4.75, units='in')

# across species, by rivers
ggplot(predGrid2Both %>% 
         filter(salmon01 == 0, cohortStrengthScaledBKT == 0, cohort == 2006, cohortStrengthScaledBNT2p5 == 0),
       aes(ydayCumul, pred, group = riverGG, color = riverGG)) +
  #geom_point() + 
  geom_vline(xintercept = c(365,365*2), color = 'grey60', linetype = 2) +
  geom_line(size = 1.1) +
  labs(y = 'Predicted body size (mm)',
       x = 'Days since age-0 Jan 1',
       color = 'River') +
  #scale_color_viridis_c() +
  theme_publication(base_size = 20) +
  theme(legend.position = c(0.125, 0.8), 
        legend.direction = "vertical",
        legend.title = element_text(face = "plain")) +
  theme(legend.text=element_text(size=12),
        legend.title=element_text(size=12)) +
  facet_grid(cols = vars(speciesGG))

ggsave('./figures/ydayCumulAcrossSppByRiver.png', width = 8, height = 4.75, units='in')
